Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-23 paper/paper.tex
added pre-flight procedures, more list fiddling

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous construction}

@@

\begin{multicols}{2}
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
%	\centering
	\item Anthony Garrison, President
	\item Amanda Gaetano, Vice President
	\item Pat Hickey, Treasurer and Electronics Team Leader
	\item Greg Quinn, Mechanical Team Leader
%\end{itemize}
%\begin{multicols}{2}
%\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
%	\centering
	\item Stephen Indyk 
	\item Cogan Noll
	\item John Palmer 
	\item Adrien Perkins
	\item Michael Varga 
	\item Bradley Lord
	\item David Wescott
	\item Taras Wallace
\end{itemize}
\end{multicols}

@@

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\hyphenation{auto-nomous construction}

@@

%\begin{multicols}{2}
%\begin{itemize}
%	\setlength{\itemsep}{0cm}
%	\setlength{\parskip}{0cm}
%	\item Anthony Garrison, President
%	\item Amanda Gaetano, Vice President
%	\item Pat Hickey, Treasurer and Electronics Team Leader
%	\item Greg Quinn, Mechanical Team Leader
%	\item Stephen Indyk 
%	\item Cogan Noll
%	\item John Palmer 
%	\item Adrien Perkins
%	\item Michael Varga 
%	\item Bradley Lord
%	\item David Wescott
%	\item Taras Wallace
%\end{itemize}
%\end{multicols}

\vspace{12 pt}

\begin{tabular}{l l}
Anthony Garrison, President & Cogan Noll \\
Amanda Gaetano, Vice President & John Palmer\\
Pat Hickey, Treasurer and Electronics Team Leader & Adrien Perkins\\
Greg Quinn, Mechanical Team leader & Michael Varga\\
Stephen Indyk & (Bradley Lord OR Taras Wallace)\\
\end{tabular}

\vspace{24 pt}

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Pre-flight Procedures}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extentions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen*, centerman**.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``reciever on''.  Centerman turns on reciever, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Prime engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.

\end{enumerate}
